% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\usepackage{multicol}
\begin{document}
    \pagenumbering{gobble} % suppress displaying page number

    \name{Zhe Li}

    \basicInfo{
        \email{lizhejiayou@foxmail.com} \textperiodcentered\
        \phone{(+86) 182-2260-09xx}
    }


    \section{\faStarO\ Summary}
    \begin{itemize}[parsep=0.5ex]
        \item Over 4 years professional experience in Android APP development.
        \item Versed in APP architecture programming, Code reorganization and modularization,
        Object-Oriented Analysis and Design.
        \item Proficient in JAVA, Kotlin, Shell, Python, and Flutter-Android hybrid development.
        \item Strong adaptability and flexibility \& Problem-solving skills.
        \item Teamwork and Collaboration \& Interpersonal and Communication Skills.
    \end{itemize}


    \section{\faGraduationCap\ Education}
    \datedsubsection{\textbf{Nankai University}, Tianjin, China}{2013 -- 2017}
    \textit{B.S.} in Information And Numerical Science


    \section{\faUsers\ Experience}
    \datedsubsection{\textbf{Beijing Yuanli Weilai Sci. \& Tech. Co.Ltd}}{Jan.2021 -- Present}
    \role{Senior Android Developer}{Worked on Xiaoyuan AI Course App team}
    \begin{itemize}
        \item Engaged in the design of Xiaoyuan AI Course App, detailing operation aspects, functions, capabilities and features.
        \item Implemented modularization design of Xiaoyuan AI Course App.
        \item Optimized architecture of video page.
    \end{itemize}

    \datedsubsection{\textbf{Beijing Yuanli Weilai Sci. \& Tech. Co.Ltd}}{Jan. 2019 -- Jan. 2021}
    \role{Android Developer}{Worked on Xiaoyuan Souti App team}
    \begin{itemize}
        \item Involved in the design of user interfaces that engaged multiple senses and produced immersive experiences.
        \item Experienced working between numerous devices and versions of Android; Responsible for AndroidX migration of app.
        \item Implemented the library of multiple push service.
        \item Optimized architecture of camera function.
    \end{itemize}

    \datedsubsection{\textbf{Samsung Tianjin Communication R\&D Co.Ltd}}{Mar. 2017 -- Jan. 2019}
    \role{Junior Android Developer}{Worked on App Framework Team}
    \begin{itemize}
        \item Responsible for Samsung mobile phone system Framework code maintenance.
        \item Participated in App Lock app's adaptation and maintenance.
        \item Passed the Samsung's highest algorithm exam (expert level).
        \item Participated in the Associate Architect Program training of Korea Suwon Samsung Human Resources Institute.
    \end{itemize}

    \section{\faFileCodeO\ Projects}
    {\setlength\multicolsep{0pt}
        \begin{multicols}{2}

            \textbf{Modularization Design of Xiaoyuan AI Course App}
            \begin{itemize}
                \item Support for multi-host integration
                \item Page route between modules
                \item Monorepo development strategy
            \end{itemize}

            \textbf{Architecture of Video Page}
            \begin{itemize}
                \item Overall framework using Redux
                \item Reusing video widget
                \item Easy to be further extended
            \end{itemize}

            \textbf{Multiple Push Service Library}
            \begin{itemize}
                \item Easy to integrate, fully document support
                \item Custom push service provider
                \item Multiple retry mechanisms
            \end{itemize}

            \textbf{Camera View Library}
            \begin{itemize}
                \item Support for camera1, camera2, and Huawei camera
                \item Improved the speed of taking photos
                \item Exception handling
            \end{itemize}

        \end{multicols}}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}


    \section{\faCogs\ Skills}
    \begin{itemize}[parsep=0.5ex]
        \item Programming Languages: Kotlin == Java > Dart > Python == Shell
        \item Platform: Android, Flutter
        \item Tools: Android Studio, Visual Studio Code, Charles, ADB, git
        \item Software Architecture: Design Pattern, Object-Oriented Programming, Modularization design
        \item Android Libraries: Retrofit, Room, EventBus, ViewBinding, Lifecycle, Kotlin Coroutine
    \end{itemize}

% \section{\faHeartO\ Honors and Awards}
% \datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
% \datedline{Other awards}{2015}

% \section{\faInfo\ Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
%   \item Blog: http://your.blog.me
%   \item GitHub: https://github.com/username
%   \item Languages: English - Fluent, Mandarin - Native speaker
% \end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
